### 2019-12-13 Draft/Draft.tex
fixed some typos

\caption{{\small \textsf{RMSE} statistics derived a 25--member {\enkf} simulation as a function of  `$\mathsf{m}$' (\tit{vertical axes}) and $\tau_\mathsf{win}$ (\tit{horizontal axes}) showing the difference between the \textsf{WCDA} and the \textsf{LACC} implementation.}}

@@

The effects of stochastic noise due to the forcing term are reduced by the averaging operation yet they are not completely removed. This leaves further room for optimisation of the {\lacc} implementation; this is achieved by adaptively inflating the cross-update by multiplying the error covariance matrix $\mathbf{P}_t$ by a time-dependent factor $\alpha_t$. In our experiments, it turns out that deflation is required instead of inflation to counter the stochasticity in the atmospheric sub-component. The mean value $\bar{\alpha}_t$ over time of the multiplicative inflationary factor  $\alpha_t$ is found to be roughly 0.8. In figure \ref{fig:8}, we can see the smoothing effect of inflation on the results of our {\rmse} statistics. We also find that deflation helps in stricter convergence of {\lacc} implementation for the same reason.

@@

\centering\includegraphics[width=75mm]{{Fig8a}.png}\vspace{0.05in}

@@

\caption{{\small \textsf{RMSE} statistics including adaptive inflation. The mean value $\bar{\alpha}_t$ of the multiplicative adaptive inflationary factor $\alpha_t$ is roughly 0.8 in our experiment.}}

>>>>

\caption{{\small \textsf{RMSE} statistics derived a 25--member {\enkf} simulation as a function of  `$\mathsf{m}$' (\tit{vertical axes}) and $\tau_\mathsf{win}$ (\tit{horizontal axes}) showing the difference between the \textsf{WCDA} and the \textsf{LACC} implementation. Top panel shows the oceanic component while the bottom panel depicts the atmosphere.}}

@@

{\noindent}The effects of stochastic noise due to the forcing term are reduced by the averaging operation yet they are not completely removed. This leaves further room for optimisation of the {\lacc} implementation; this is achieved by adaptively inflating the cross-update by multiplying the error covariance matrix $\mathbf{P}_t$ by a time-dependent factor $\alpha_t$. In our experiments, it turns out that deflation is required instead of inflation to counter the stochasticity in the atmospheric sub-component. The mean value $\bar{\alpha}_t$ over time of the multiplicative inflationary factor  $\alpha_t$ is found to be roughly 0.8. In figure \ref{fig:8}, we can see the smoothing effect of inflation on the results of our {\rmse} statistics. We also find that deflation helps in stricter convergence of {\lacc} implementation for the same reason.

@@

\centering\includegraphics[width=75mm]{{Fig8a}.png}

@@

\caption{{\small \textsf{RMSE} statistics including adaptive inflation. The mean value $\bar{\alpha}_t$ of the multiplicative adaptive inflationary factor $\alpha_t$ is roughly 0.8 in our experiment. Left panel shows the oceanic component while the right panel depicts the atmosphere.}}
